Running `Earth_obs_cleaning` on MCD19A2: Results from CONUS

### 2022-12-20 R/CONUS_AOD.Rmd
call error envelope in CONUS_AOD

```{r error_envelope, echo=FALSE}
# error envelope for MAIAC is equivalent to that reported in AMT MAIAC publication
dt[, round(100 * proportions(table(y.sat > (y.ground - 0.05 - 0.1*y.ground) & y.sat < (y.ground + 0.05 + 0.1*y.ground))))]
# sure looks like we would have a much smaller error envelope (in both additive and multiplicative terms)
dt[, round(100 * proportions(table(y.ground.pred > (y.ground - 0.025 - 0.055*y.ground) & y.ground.pred < (y.ground + 0.025 + 0.055*y.ground))))]

```

>>>>

```{r error_envelope, echo=TRUE}
# error envelope for MAIAC is equivalent to that reported in AMT MAIAC publication
dt[, round(100 * proportions(table(y.sat > (y.ground - 0.05 - 0.1*y.ground) & y.sat < (y.ground + 0.05 + 0.1*y.ground))))]
# sure looks like we would have a much smaller error envelope (in both additive and multiplicative terms)
dt[, round(100 * proportions(table(y.ground.pred > (y.ground - 0.025 - 0.055*y.ground) & y.ground.pred < (y.ground + 0.025 + 0.055*y.ground))))]

# now with our error envelope function
system.time(envelope <- empirical.error.envelope(dt)); head(envelope)
```
